Multiphysics Core Dynamics Simulation Using the Improved Quasi-Static Method

### 2017-06-01 doc/M&C_2017/Presentation/MC2017_Presentation.tex
Presentation Final Draft

\logo{\includegraphics[height=0.8cm]{figures/IUP_Logo.jpeg}\includegraphics[height=0.8cm]{figures/TAM-logo.png}}

@@

\column{.5\textwidth}
\begin{table}
\captionsetup{font=scriptsize}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{Implicit Discretization}\\
\hline
Run  &  $\Delta t$ & Error & Runtime (hr) & Linear Iter.\\
\hline
1	& 4.0e-3	& 1.407e-2 	& 4.11	& 7.13e4	\\
2	& 2.0e-3	& 3.174e-3 	& 6.01	& 9.49e4 	\\
3 	& 1.0e-3 	& 7.690e-4 	& 10.38	& 1.45e5	\\
4 	& 5.0e-4 	& 1.892e-4 	& 21.91	& 2.08e5	\\
5 	& 2.5e-4	& 4.590e-5 	& 25.23	& 3.16e5	\\
\hline
\end{tabular}}}
\end{center}
\end{table}
\vspace{-7mm}

\begin{table}
\captionsetup{font=small}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{IQS}\\
\hline
	&  Temperature 	&  		& Runtime 	& \% Increase	\\
Run	&  Updates 	& Error & (hr)		& in Runtime$^*$\\
\hline
1	& 1		& 2.612e-3 	& 3.96 	& -3.18\%	\\
2	& 2		& 9.893e-4 	& 6.02	&  47.1\%	\\
3 	& 4 	& 5.796e-4 	& 7.87	&  92.3\%	\\
4 	& 8 	& 4.772e-4 	& 12.61	& 207.9\% 	\\
5 	& 16	& 4.516e-4 	& 22.14	& 440.7\%	\\
\hline
\end{tabular}}}
\end{center}
\end{table}
\vspace{-7mm}

\begin{table}
\captionsetup{font=scriptsize}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{IQS P-C}\\
\hline
	&  Temperature 	&  		& Runtime 	& \% Increase	\\
Run	&  Updates 	& Error & (hr)		& in Runtime$^*$\\
\hline
1	& 1		& 3.488e-3 	& 2.91 	& -28.9\%	\\
2	& 2		& 1.349e-3 	& 3.73	& -9.00\%	\\
3 	& 4 	& 9.161e-4 	& 3.97	& -3.04\%	\\
4 	& 8 	& 8.052e-4 	& 5.39	&  31.7\%	\\
5 	& 16	& 7.905e-4 	& 8.19	&  100\%	\\
\hline
\end{tabular}}}
%}
\\
\tiny $^*$ runtime difference from $\Delta t = 0.004$ implicit dis.
\end{center}
\end{table}

@@

\begin{block}{Accuracy and Runtime}
\begin{center}
\resizebox{\linewidth}{!}{
\begin{tabular}{|l|ccc|}
\hline
Method & No. of Steps & \% Increase Runtime$^*$ & Max Power Error \\
\hline
Implicit Dis. 		& 300 &	---		&	7.875e-4	\\
IQS 				& 300 & -11.9\%	&	8.385e-5	\\
IQS (5 updates) 	& 300 &  49.7\%	&	3.687e-5	\\
IQS P-C 			& 300 &  -2.1\%	&	7.527e-4	\\
IQS P-C (5 updates) & 300 &  26.5\%	&	1.227e-4	\\
\hline
\end{tabular}
}
\end{center}
\vspace{-3mm}
$^*$ difference in runtime from implicit discretization 
\end{block}

@@

\begin{figure}
\includegraphics[height=0.5in]{figures/thank_you.png}
\end{figure}

\begin{figure}
\includegraphics[height=2.5in]{figures/nuclear_collage.png}
\hspace{5mm}
\includegraphics[height=2.5in]{figures/tamu_atom.jpg}
\end{figure}

>>>>

%\logo{\includegraphics[height=0.8cm]{figures/IUP_Logo.jpeg}\includegraphics[height=0.8cm]{figures/TAM-logo.png}}

@@

\column{.5\textwidth}
\vspace{-5mm}
\begin{table}
\captionsetup{font=scriptsize}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{Implicit Discretization}\\
\hline
Run  &  $\Delta t$ & Error & Runtime (hr) & Linear Iter.\\
\hline
1	& 4.0e-3	& 1.407e-2 	& 4.11	& 7.13e4	\\
\hline
\rowcolor{yellow} 2	& 2.0e-3	& 3.174e-3 	& 6.01	& 9.49e4 	\\
\hline
\rowcolor{green} 3 	& 1.0e-3 	& 7.690e-4 	& 10.38	& 1.45e5	\\
\hline
4 	& 5.0e-4 	& 1.892e-4 	& 21.91	& 2.08e5	\\
5 	& 2.5e-4	& 4.590e-5 	& 25.23	& 3.16e5	\\
\hline
\end{tabular}}}
\end{center}
\end{table}
\vspace{-7mm}

\begin{table}
\captionsetup{font=small}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{IQS}\\
\hline
	&  Temperature 	&  		& Runtime 	& \% Increase	\\
Run	&  Updates 	& Error & (hr)		& in Runtime$^*$\\
\hline
\rowcolor{yellow} 1	& 1		& 2.612e-3 	& 3.96 	& -3.18\%	\\
\hline
2	& 2		& 9.893e-4 	& 6.02	&  47.1\%	\\
3 	& 4 	& 5.796e-4 	& 7.87	&  92.3\%	\\
4 	& 8 	& 4.772e-4 	& 12.61	& 207.9\% 	\\
5 	& 16	& 4.516e-4 	& 22.14	& 440.7\%	\\
\hline
\end{tabular}}}
\end{center}
\end{table}
\vspace{-7mm}

\begin{table}
\captionsetup{font=scriptsize}
\begin{center}
\colorbox{white}{\resizebox{\textwidth}{!}{
\begin{tabular}{|l|l|ccc|}
\hline
\multicolumn{5}{|c|}{IQS P-C}\\
\hline
	&  Temperature 	&  		& Runtime 	& \% Increase	\\
Run	&  Updates 	& Error & (hr)		& in Runtime$^*$\\
\hline
1	& 1		& 3.488e-3 	& 2.91 	& -28.9\%	\\
2	& 2		& 1.349e-3 	& 3.73	& -9.00\%	\\
\hline
\rowcolor{green} 3 	& 4 	& 9.161e-4 	& 3.97	& -3.04\%	\\
\hline
4 	& 8 	& 8.052e-4 	& 5.39	&  31.7\%	\\
5 	& 16	& 7.905e-4 	& 8.19	&  100\%	\\
\hline
\end{tabular}}}
%}
\\
\tiny $^*$ runtime difference from $\Delta t = 0.004$ implicit dis.
\end{center}
\end{table}

@@

\begin{block}{Accuracy and Runtime}
\begin{center}
\resizebox{\linewidth}{!}{
\begin{tabular}{|l|ccc|}
\hline
Method & No. of Steps & \% Increase Runtime$^*$ & Max Power Error \\
\hline
Implicit Dis. 		& 300 &	---		&	7.875e-4	\\
\hline
\rowcolor{yellow} IQS 				& 300 & -11.9\%	&	8.385e-5	\\
\hline
IQS (5 updates) 	& 300 &  49.7\%	&	3.687e-5	\\
IQS P-C 			& 300 &  -2.1\%	&	7.527e-4	\\
\hline
\rowcolor{green} IQS P-C (5 updates) & 300 &  26.5\%	&	1.227e-4	\\
\hline
\end{tabular}
}
\end{center}
\vspace{-3mm}
$^*$ difference in runtime from implicit discretization 
\end{block}

@@

%-------------------------------------------------------------------
\begin{frame}{Acknowledgments}

\begin{block}{}
\begin{itemize}
\item This material is based upon work supported under an Integrated University Program Graduate Fellowship
\begin{figure}
\includegraphics[height=0.5in]{figures/IUP_Logo.jpeg}
\end{figure}
\item Any opinions, findings, conclusions or recommendations expressed in this publication are those of the author(s) and do not necessarily reflect the views of the Department of Energy Office of Nuclear Energy
\end{itemize}
\end{block}

\begin{figure}
\includegraphics[height=0.5in]{figures/tamune_logo.png}
\end{figure}
\begin{figure}
\includegraphics[height=0.5in]{figures/INL_logo.png}
\end{figure}
